\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage{xcolor} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level
\usepackage{caption}
\captionsetup[table]{skip=11pt} %sets a space after table caption
\usepackage{times}
\usepackage{tabto} %general tabbed spacing
\usepackage{longtable} %need to put label at top under caption then \\ - use spacing
\usepackage[stable,hang,flushmargin]{footmisc} %footnotes in section titles and no indent
\usepackage[round]{natbib} %parenthesis instead of brackets for inline citations
\usepackage{enumitem}
\usepackage{boldline}
\usepackage{makecell}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{array}
\usepackage{caption}
\usepackage[labelfont=bf]{caption}
\usepackage{chngcntr}
\usepackage{hyperref}

\newcommand{\edit}[1]{\textcolor{blue}{#1}} %shortcut for changing font color on revised text
\newcommand{\fn}[1]{\footnote{#1}} %shortcut for footnote tag
\newcommand*\sq{\mathbin{\vcenter{\hbox{\rule{.3ex}{.3ex}}}}} %makes a small square as a separator $\sq$
\renewcommand\labelenumi{(\theenumi)} %changes 1. to (1) in enumerated list

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
\renewcommand{\headrulewidth}{0.5pt} %turn off line in header
\lhead{\scriptsize TM529 - Risk assessment}
\chead{\scriptsize \today}
\rhead{\scriptsize Project 2 - Probability and statistics}
\rfoot{\thepage}

\begin{filecontents}{references.bib}
    @misc{
        ,
        author = {{}},
        title = {{}},
        year = {}
    }
    @article{
        ,
        author = {{}},
        journal = {},
        pages = {},
        title = {{}},
        volume = {},
        year = {}
    }
    @techreport{
        ,
        author = {{}},
        title = {{}},
        year = {},
        institution = {},
        number = {}
    }
\end{filecontents}

\begin{document}

\begin{titlepage}
    \title{
        TM529 - Risk assessment\\
        Project 2 - Probability and statistics\\
    }
    \author{
        Name
        \\ \\ \\
        University of Idaho $\sq$ Idaho Falls Center for Higher Education
        \\ \\
        Nuclear Engineering and Industrial Management Department
        \\ \\ \\
        email 
    }
\clearpage %not have page number on title page
\maketitle
\vspace*{\fill}
\begin{flushright}{
        Total - 200
}
\end{flushright}
\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

\begin{enumerate}[leftmargin=*,topsep=0pt,font=\bfseries]
    \item\textbf{(30) What is the \textit{probability of dying} for a six player Russian roulette game for a six chamber gun, but the chamber is \textit{respun} after every attempt \textit{if the shooter does not die.} Show when the probabilities converge, and where the ‘best’ seat is at the table.}
        \vspace{\baselineskip}
    
        
        
        
        
        
        
        
        
        
        
        
        
        
        \newpage
    \item\textbf{(30) Derive and plot the discrete probability density function for two dice.}
        \vspace{\baselineskip}
        
        
        
        
        
        
        
        
        
        
        
        
        
        
        \newpage
    \item\textbf{(30) The Poisson distribution describes radioactive decay. It is a specific form of the binomial distribution. Derive the Poisson distribution from the binomial distribution. Derive the first and second moments of the Poisson distribution. Briefly comment on their significance and implications. (\textit{It should be obvious if you do it right.})}
        \vspace{\baselineskip}

        
        
        
        
        
        
        
        
        
        
        
        
        

        
        
        \newpage
    \item\textbf{(50) Design a spam filter based on Bayesian reasoning by devising a list of 10-15 words that would indicate a message is likely to be spam. Likely = 80\% probability. \href{https://courses.lumenlearning.com/uidaho-riskassessment/chapter/bayes-theorem/}{See the OER for a starting example.}}
        \vspace{\baselineskip}

















        \newpage
    \item\textbf{(30) Marie is getting married tomorrow (\textit{third time is a charm}), at an outdoor ceremony in the desert because reasons. In recent years, at the location of the ceremony, it has rained only 5 days each year. Unfortunately, the weatherman has predicted rain for tomorrow. When it actually rains, the weatherman had correctly forecast rain 90\% of the time. When it did not rain, he incorrectly forecast rain 10\% of the time. What is the probability that it will rain on the day of the wedding?}
        \vspace{\baselineskip}

















        \newpage
    \item\textbf{(30) Late, late one night in a bar in Las Vegas you meet a guy who claims to know that in the casino at the Tropicana there are two sorts of slot machines: one that pays out 3\% of the time, and one that pays out 25\% of the time. The two types of machines are colored red and blue. The only problem is, the guy is so drunk he does not remember which is which. You go to the Tropicana to find out more. You find a red and a blue machine side by side. You toss a coin to decide which machine to try first; noting the outcome, you then put the coin into the red machine. It (red) does not pay out. How should you update your estimate of the probability that this (red) is the high payout machine? What if it had paid out - what would be your new estimate then? Consider how many times you would have to fail to get a payout from the red machine before saying you're 90\% confident it is not the high payout machine.}
        \vspace{\baselineskip}

















\end{enumerate}

\newpage 

\bibliographystyle{ieeetr}
\setlength{\bibhang}{0pt}
\bibliography{references}

\end{document}
